This is a R markdown file for peer assesment 1.

Read the data
```{r}
walk <- read.csv("activity.csv")
```

Declare Variables.

```{r}
SumSet <- numeric()
AvgSet <- numeric()
MedSet <- numeric()
minSet <- numeric()
SumSet1 <- numeric()
AvgSet1 <- numeric()
MedSet1 <- numeric()
daySet <- character()
```

Question 1 - What is mean total number of steps taken per day?

```{r}
for(day in 0:60)
{
days <- as.Date("2012-10-01") + day
daywalk <- subset (walk, date == as.character(days))
Dayna <- na.omit(daywalk[[1]])
DaySum <- sum(Dayna)
SumSet = append(SumSet, DaySum, after=length(SumSet))
DayAvg <- mean(Dayna)
AvgSet = append(AvgSet, DayAvg, after=length(AvgSet))
DayMed <- median(Dayna)
MedSet = append(MedSet, DayMed, after=length(MedSet))
}
hist(SumSet)
```
Vector showing the mean number of steps taken per day
```{r}
print(AvgSet)
```
Vector showing the median number of steps taken per day
```{r}
print(MedSet)
```

Question 2 - What is the average daily activity pattern?
```{r}
for (i in seq(0,2355,5))
{
times <- subset(walk,interval == i)
minsteps <- na.omit(times[[1]])
minsteps1 <- sum(minsteps)
minSet = append(minSet, minsteps1, after=length(minSet))
if(minsteps1 == max(minSet))
{
maxtime <- i} 
}
tsSet <- ts(minSet)
plot(tsSet, type="l")
```
What is the maximum number of steps taken?
```{r}
maxvalue <- max(minSet)
print(maxvalue)
```
What is the time point when maximum number of steps were taken?

```{r}
print(maxtime)
```

Question 3 - Imput missing value.
I replaced the missing value with "1" and then calculated the mean, median and sum of number of steps taken each day.
```{r}
walk1 <- walk
walk1[is.na(walk1)]<-1
for(day1 in 0:60)
{
days1 <- as.Date("2012-10-01") + day1
daywalk1 <- subset (walk1, date == as.character(days1))
DaySum1 <- sum(daywalk1[[1]])
SumSet1 = append(SumSet1, DaySum1, after=length(SumSet1))
DayAvg1 <- mean(daywalk1[[1]])
AvgSet1 = append(AvgSet1, DayAvg1, after=length(AvgSet1))
DayMed1 <- median(daywalk1[[1]])
MedSet1 = append(MedSet1, DayMed1, after=length(MedSet1))
}
hist(SumSet1)
```
Vector showing the mean number of steps taken per day
```{r}
print(AvgSet1)
```
Vector showing the median number of steps taken per day
```{r}
print(MedSet1)
```
Question 4 - Are there differences in activity patterns between weekdays and weekends?

for(day1 in 0:60)
{
days1 <- as.Date("2012-10-01") + day1
daytype <- weekdays(days1)
if(daytype == c("Monday","Tuesday", "Wednesday", "Thursday", "Friday"))
{daytype1 <- 0}
else if(daytype == c("Saturday","Sunday"))
{daytype1 <- 1}
daySet <- append(daySet,daytype1,after = length(daySet))
}
daytype.f <- factor(daySet, labels = c("Weekday","Weekend"))



for (i in seq(0,2355,5))
{
times <- subset(walk1,interval == i)
minsteps <- na.omit(times[[1]])
minsteps1 <- sum(minsteps)
minSet = append(minSet, minsteps1, after=length(minSet))
if(minsteps1 == max(minSet))
{
maxtime <- i} 
}
maxvalue <- max(minSet)
print(maxvalue)
print(maxtime)
tsSet <- ts(minSet)
plot(tsSet, type="l")
